|

### 2023-05-15 paper/01-introduction.Rmd
Small edits.

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool in sports analytics.
Numerous sports have been collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This spatio-temporal multi-resolution source of data have provided exceptional opportunities for researchers to perform advanced studies at a more complex level to deepen the understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

@@

In an attempt to foster analytics and innovate the game, the National Football League (NFL) introduced their player tracking system known as Next Gen Stats (NGS) in 2016 [@nfl2023ngs].
NGS uses radio frequency identification (RFID) chips placed in players' shoulder pads (and in the ball) to collect data at a rate of 10 frames per second.
The data captures real-time on-field information such as locations, speeds, and accelerations of all 22 players (as well as the ball).
While these data were initially only available for teams, media, and vendors, in December 2018 the NFL launched the inaugural edition of their annual Big Data Bowl (BDB) competition [@nfl2023big].

The first BDB led to several contributions largely focused on offensive performance evaluation. For example, one group of finalists introduced an approach for modeling the hypothetical completion probability of a pass aiding in the evaluation of quarterback (QB) decision making [@deshpande2020expected]. The winners of the inaugural BDB focused on identifying receiver routes via clustering techniques [@chu2020route] and convolutional neural networks [@sterken2019routenet]. Along with the BDB competition entries, the public release of NGS data allowed researchers to tackle <!-- (pun intended) --> a variety of other problems such as revisiting fourth down decision making [@lopez2020bigger], annotating pass coverage with Gaussian mixture models [@dutta2020unsupervised], and introducing a continuous-time framework to estimate within-play value [@yurko2020going].  Since its inception, the BDB has chosen a different theme each year leading to new insight about evaluating different positions such as running backs, defensive backs, and special teams. The 2023 edition of the NFL Big Data Bowl asked participants to evaluate linemen on passing plays [@Howard2023NFL].

@@

Perhaps the most commonly-known statistics for evaluating defensive linemen on pass rush plays are sacks, hits, and hurries, which are discretely observed at the play-level.
Officially tracked by the NFL since 1982, a sack is recorded when a defender tackles the QB behind the line of scrimmage before the QB releases a pass. 
Other traditional box score statistics such as hits and hurries are collected by various outlets. 
A hit is a collision between a defender and the opposing team's quarterback while the QB is in possession of the ball.
A hurry represents an instance when a defender successfully disrupts without necessarily making direct contact with the QB and forces the QB to make a throw earlier than expected.
These are all simple binary measures of pass rush outcome for any given play.
However, for plays that do not result in the aforementioned outcomes (in particular, sack), there are still many intermediate defensive actions on the field within the play that are valuable and can be considered positive achievements.

Moreover, the sum of sacks, hits, and hurries is often defined as pressures.
This is better than the individual counts to some extent, but suffers from problems of subjectivity (e.g., whether there is an actual hurry or not).
Pro football focus (PFF) comes up with a metric called pass-rush productivity (PRP), which is a minor modification from the aforementioned pressures metric (see Table \ref{tab:metrics}).
In particular, PRP gives twice as much weight to a sack relative to hurries and hits, which is a small upgrade to pressures.
However, the choice of weights is ad-hoc and still only indicates binary outcomes, similar to the shortcomings of previous metrics.

>>>>

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art in sports analytics.  Numerous sports are collecting and releasing data on player and ball locations on the playing surface over the course of a game. This spatio-temporal multi-resolution source of data has provided exceptional opportunities for researchers to perform advanced studies at a more granular level to deepen our understanding of different sports.  For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

@@

In an attempt to further develop analytics and innovate the game, the National Football League (NFL) introduced their player tracking system known as Next Gen Stats (NGS) in 2016 [@nfl2023ngs].
NGS uses radio frequency identification (RFID) chips placed in players' shoulder pads (and in the ball) to collect data at a rate of 10 frames per second.
The data captures real-time on-field information such as locations, speeds, and accelerations of all 22 players (as well as the ball).
While these data were initially only available for teams, media, and vendors, in December 2018 the NFL launched the inaugural edition of their annual Big Data Bowl (BDB) competition [@nfl2023big].

The first BDB led to several contributions largely focused on offensive performance evaluation. For example, one group of finalists introduced an approach for modeling the hypothetical completion probability of a pass aiding in the evaluation of quarterback (QB) decision making [@deshpande2020expected]. The winners of the inaugural BDB focused on identifying receiver routes via clustering techniques [@chu2020route] and convolutional neural networks [@sterken2019routenet]. Along with the BDB competition entries, the public release of NGS data allowed researchers to tackle <!-- (pun intended.  #eyeroll) --> a variety of other problems such as revisiting fourth down decision making [@lopez2020bigger], annotating pass coverage with Gaussian mixture models [@dutta2020unsupervised], and introducing a continuous-time framework to estimate within-play value [@yurko2020going].  Since its inception, the BDB has chosen a different theme each year leading to new insight about evaluating different positions such as running backs, defensive backs, and special teams. The 2023 edition of the NFL Big Data Bowl asked participants to evaluate linemen on passing plays [@Howard2023NFL].

@@

Perhaps the most commonly-known statistics for evaluating defensive linemen on pass rush plays are sacks, hits, and hurries, which are discretely observed at the play-level.
Officially tracked by the NFL since 1982, a sack is recorded when a defender tackles the QB behind the line of scrimmage before the QB releases a pass. 
Other traditional box score statistics such as hits and hurries are collected by various outlets. 
A hit is a collision between a defender and the opposing team's quarterback while the QB is in possession of the ball.  <!-- This is a sack, right? -->
A hurry represents an instance when a defender successfully disrupts without necessarily making direct contact with the QB and forces the QB to make a throw earlier than expected.
These are all simple binary measures of pass rush outcome for any given play.
However, for plays that do not result in the aforementioned outcomes (in particular, sack), there are still many intermediate defensive actions on the field within the play that are valuable and can be considered positive achievements.

In addition to these individual binary metrics, the sum of sacks, hits, and hurries is often defined as pressures.
This is better than the individual counts to some extent, but suffers from problems of subjectivity (e.g., whether there is an actual hurry or not).
Pro football focus (PFF) defines a metric called pass-rush productivity (PRP), which is a minor modification from the aforementioned pressures metric (see Table \ref{tab:metrics}).
In particular, PRP gives twice as much weight to a sack relative to hurries and hits, which is a small upgrade to pressures, however, the choice of weights is ad-hoc and still only copnsiders binary outcomes, similar to the shortcomings of previous metrics.
